---
title: "Workshop Demo Doc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Demo doc (part 1): Try it out!

Let's first load the tidyverse suite of packages.

If you haven't already, make sure to install the tidyverse, first.

*You can skip this code "chunk" if you already have the tidyverse installed; you only need to do this once*

```{r}
install.packages("tidyverse")
```

Be sure to run this next line to load the tidyverse. You do this each time you open R.

```{r}
library(tidyverse)
```

Here is the data set we will use:

```{r}
gss_cat
```

# Select

Let's select only a few variables.

```{r}
gss_cat %>% 
  select(year, marital, tvhours)
```

**Try it out!**

Now, select three *different* variables, and run the code chunk to view the result.

```{r}
gss_cat %>% 
  select()
```

# Filter

```{r}
gss_cat %>% 
  filter(age > 30)
```

**Try it out!**

Filter to include only those individuals who watch a lot of TV - more than 10 hours per *day*!

Be sure to run the result to see whether it did what you think it should do!

```{r}
gss_cat %>% 
  
```

# Mutate

Let's create a new variable for those 60 years of age or older.

```{r}
gss_cat %>% 
  mutate(potential_senior = if_else(age >= 60, TRUE, FALSE))
```